Generating Interactive WebSocket Applications in TypeScript

### 2020-03-09 PLACES_2020/encoding.tex
PLACES: remove VDOM paragraph

\fz{Is VDOM needed to be covered here?}

\am{Intended to motivate how the session runtime implementation renders the required state and the VDOM deals with the diffs - at the same time, unsure whether this is important for the reader to understand (or just leave the DOM rendering as a black box)?}
\paragraph{Virtual DOM (VDOM)}
React components are rendered on a logical
abstraction of the DOM, which in turn performs a \texttt{diff} on the current
browser DOM and patches the delta accordingly.
This allows the developer to
directly specify what should be rendered without having to worry about which
elements to append or remove from the browser DOM.

@@

For browser-side targets, we extend the approach presented in \cite{MVU2019} on
\textit{multiple model types} motivated by the \textit{Model-View-Update} (MVU)
architecture.
% FEEDBACK: introduce MVU and model type
An MVU application features a \textit{model} encapsulating application
state, a \textit{view function} rendering the state on the DOM, and an
\textit{update function} handling \textit{messages} produced by the
rendered model to produce a new model.
The concept of model types express type dependencies between these
components: a \emph{model type} uniquely defines a \textit{view function},
set of \textit{messages} and \textit{update function} -- rather than
producing a new model, the update function defines valid transitions to
other model types.
We leverage the correspondence between model types and states in the EFSM:
each state in the EFSM is a model type, the set of messages represent
the possible (IO) actions available at that state,
and the update function defines which successor state to transition to,
given the supported IO actions at this state.

>>>>

@@

For browser-side targets, we extend the approach presented in \cite{MVU2019} on
\textit{multiple model types} motivated by the \textit{Model-View-Update} (MVU)
architecture.
% FEEDBACK: introduce MVU and model type
An MVU application features a \textit{model} encapsulating application
state, a \textit{view function} rendering the state on the Document Object Model (DOM), and an
\textit{update function} handling \textit{messages} produced by the
rendered model to produce a new model.
The concept of model types express type dependencies between these
components: a \emph{model type} uniquely defines a \textit{view function},
set of \textit{messages} and \textit{update function} -- rather than
producing a new model, the update function defines valid transitions to
other model types.
We leverage the correspondence between model types and states in the EFSM:
each state in the EFSM is a model type, the set of messages represent
the possible (IO) actions available at that state,
and the update function defines which successor state to transition to,
given the supported IO actions at this state.
